Mapping parishe emissions: Framlingham as an example

### 2021-09-13 mappingParishes.Rmd
fixed typos & added n meters changes

Npw build a simple map from LSOAs based on the Framlingham electoral ward to see how well it matches the parish (Figure \@ref(fig:simpleLSOAMap).

@@

@@

>>>>

Now build a simple map from LSOAs based on the Framlingham electoral ward to see how well it matches the parish (Figure \@ref(fig:simpleLSOAMap).

@@

gas_meters_diff = sum(fram_gas2019_dt$`Number of consuming meters`)-sum(fram_gas2010_dt$`Number of meters`)
gas_meters_diff_pc <- 100*(gas_meters_diff/sum(fram_gas2010_dt$`Number of meters`))
message("Change in number of meters = ", gas_meters_diff , " (", round(gas_meters_diff_pc)," %)")

@@

elec_meters_diff = sum(fram_elec2019_dt$`Total number of domestic electricity meters`)-sum(fram_elec2010_dt$`Total number of domestic electricity meters`)
elec_meters_diff_pc <- 100*(elec_meters_diff/sum(fram_elec2010_dt$`Total number of domestic electricity meters`))
message("Change in number of meters = ", elec_meters_diff , " (", round(elec_meters_diff_pc)," %) - should probably be about the same as number of gas meters until new builds with electricity only are more common")
